Dynamics of isoflurane-induced vasodilation and blood flow of cerebral vasculature revealed by multi-exposure speckle imaging

### 2021-08-19 article.tex
Standardized CRediT formatting

\section*{CRediT Statement}
\textbf{Colin T. Sullender:} Conceptualization, Methodology, Software, Validation, Investigation, Data Curation, Formal Analysis, Writing - Original Draft, and Visualization. \textbf{Lisa M. Richards:} Conceptualization, Methodology, Investigation, Data Curation, Writing - Review \& Editing. \textbf{Fei He:} Investigation, Resources, Writing - Review \& Editing. \textbf{Lan Luan:} Writing - Review \& Editing, Supervision, and Funding Acquisition. \textbf{Andrew K. Dunn:} Conceptualization, Writing - Review \& Editing, Supervision, Funding Acquisition, and Project Administration.

>>>>

\section*{CRediT Statement}
\textbf{Colin T. Sullender:} Conceptualization, Methodology, Software, Validation, Investigation, Data Curation, Formal Analysis, Writing - Original Draft, and Visualization. \textbf{Lisa M. Richards:} Conceptualization, Methodology, Investigation, Data Curation, and Writing - Review \& Editing. \textbf{Fei He:} Investigation, Resources, and Writing - Review \& Editing. \textbf{Lan Luan:} Writing - Review \& Editing, Supervision, and Funding Acquisition. \textbf{Andrew K. Dunn:} Conceptualization, Writing - Review \& Editing, Supervision, Funding Acquisition, and Project Administration.
